\Large \bf Cyclone: High Availability for Persistent Key Value Stores

### 2017-08-10 paper/paper.tex
Updates.

Cyclone integrates with key value stores as both a client and server side
library. Cyclone replicates the key value store across a set of replica
servers. The client side library sends \emph{all} requests to a distinguished
leader replica.  On the server side Cyclone accepts requests from clients, calls
into the key value store, and returns a response to the client. Before
executing any PUT or DELETE request, Cyclone appends it to a durable log and replicates
the request to the logs of follower replicas. The request is considered
replicated once acknowledged by a majority of replicas. Follower replicas apply
updates from the log in order.

@@

@@

Cyclone takes a software only approach to improving replication performance
using commodity network hardware. In contrast, Mojim~\cite{mojim} pairs directly
attached persistent memory with RDMA to replicate persistent data
structures. Mojim is a weak replication scheme in that none of the numerous
\emph{evaluated} modes of Mojim provide any means to keep more than two replicas
in strong synchronization. Mojim's multi-tiered replication could lose committed
updates and therefore its guarantees are too weak to be used as a replacement
for RocksDB's write ahead log. Further, Mojim's claim that
``Paxos-like protocols'' require two networking round trips and are
therefore somehow inefficient compared to mirroring is not true. For instance,
we have demonstrated with Cyclone, where the leader responds as soon as it hears
back from a majority quorum, that the critical path to replication is just one
network round trip.  A performance comparison with Mojim is hard, since it is
designed for the (hypothetical) scenario where there is enough persistent memory
to hold all persistent data, while Cyclone is designed for the more practical
case where both the write-ahead log and key value store data structures need to 
be maintained largely on flash. Nevertheless we can compare their replication
performance for the case where we use only the NVM log in Cyclone. On 40Gbps
infiniband, Mojim reported being able to mirror data at 4GB/s. In contrast,
Cyclone can replicate data three ways using 4*10 Gbps commodity ethernet NICs at
roughly 3.7 GB/s. Note that this result is with Cyclone running the provable
RAFT consensus protocol, while Mojim is doing simple mirroring of main memory.
One can conclude that network offload via RDMA and Infiniband is not an a-priori
requirement for high throughput replication. This is made possible by Cyclone's
approach that relieves the CPU from the burden of data copies. On the other
hand, the latency of a hop on commodity ethernet at 5 us with our DPDK stack is
larger than the close to 2us latency with Infiniband. Depending on the use case
for the key value store application the extra 6us with ethernet for the round
trip to the replica might be a concern for some. We note that mapping the
commutativity of key value store interfaces to multiple logs in Cyclone is a
technique that can also be applied to RDMA. Mojim confirms that concurrency is a
significant determinant of performance when replicating over RDMA.

Consensus in a box~\cite{consensus_box} implements the Zookeeper atomic
broadcast protocol together with a NIC on an FPGA. That work ignored durability,
focusing purely on network performance for replication. Latency is excellent due
to the fact that FPGA cuts out the path from CPU caches to the NIC. Authors
report latency as low as 3us for a round trip from leader to follower replica,
compared to the 6us we observe with DPDK. Notably however they reported 7us when
using TCP/IP from the FPGA rather than their own connection oriented network
protocol. On the other hand their peak replication throughput is 4M
replications/sec on 66 Gbps of aggregate network bandwith for small messages,
comparable to the 6M replications/sec mark obtained by Cyclone on an aggregate
40 Gbps of network bandwidth when \emph{also persisting the log on the SSD}. We
believe the general applicability afforded by our software only approach
together with the fact that we provide persistence by design makes it a
compelling alternative to an FPGA based solution, even given the larger
latency. Also, these results demonstrate that a general purpose CPU core can be
as efficient as an FPGA in running a consensus protocol using the techniques
described in this paper.

DARE~\cite{dare} implements state machine replication over RDMA, using a custom
replication protocol. DARE does not consider persistence in its design. It is
worthwhile to point out that since DARE allows any replica to become the leader
it requires a log adjustment protocol for the leader to bring its logs up to
date, a situation we avoid by using RAFT as described in
Section~\ref{sec:dm}. Using 40 Gb/s speeds, and 3-way replication DARE reported
being able to replicate 500K requests/sec. This is without persisting the log of
updates. In contrast, Cyclone replicates upwards of 6 million similarly sized
requests per second with 4*10 Gbps ethernet (without the second level
flashlog). DARE reports an unloaded write latency of 15us, which is lower than
the unloaded write latency of Cyclone at 20us, thanks to infiniband. The
conclusions we can draw are similar to the comparison with Mojim: a carefully
implemented log replication system obviates the need for network offload when
doing replication.

@@

Cyclone provides a client library that automatically times out and retries
requests to deal with failure. We do not provide exactly once semantics as we
believe that exactly once semantics are better provided by the key value store
itself by persisting necessary request markers - as done in systems such as
Kafka~\cite{kafka}. A possible direction of future work however is to add
exactly once semantics to Cyclone's client-server protocol itself to serve as a
building block for distributed transactions across key-value shards, each
running Cyclone, in a manner similar to other systems~\cite{raft_lin}.

>>>>

Cyclone integrates with key value stores as both a client and server side
library. Cyclone replicates the key value store across a set of replica
servers. The client side library sends \emph{all} requests - reads and updates -
to a distinguished leader replica.  On the server side Cyclone accepts requests
from clients, calls into the key value store, and returns a response to the
client. Before executing any PUT or DELETE request, Cyclone appends it to a
durable log and replicates the request to the logs of follower replicas. The
request is considered replicated once acknowledged by a majority of
replicas. Follower replicas apply updates from the log in order.

@@

We note that spreading keys across the physical logs \emph{does not} break
referential integrity. If key1 is updated followed by key2 and key2 refers to
key1, even in the face of failure linearizability in Cyclone ensures that key1
is available once key2 is seen by a client. This is true even if key1 is not
committed yet at the leader replica, since we execute reads in FIFO order with
pending entries in the log (Section~\ref{sec:sysarch}).

@@

Cyclone takes a software only approach to improving replication performance
using commodity network hardware. In contrast, Mojim~\cite{mojim} pairs directly
attached persistent memory with RDMA to replicate persistent data
structures. None of the \emph{evaluated} modes of Mojim provide any means to
keep more than two replicas in strong synchronization and therefore its
guarantees are weak compared to Cyclone.  Further, Mojim's claim that
``Paxos-like protocols'' require two networking round trips and are therefore
somehow inefficient compared to mirroring is not true. For instance, we have
demonstrated with Cyclone, where the leader responds as soon as it hears back
from a majority quorum, that the critical path to replication is just one
network round trip. We can compare Mojim's replication performance to Cyclone
for the case where we use only the NVM log in Cyclone. On 40Gbps Infiniband,
Mojim reported being able to mirror data at 4GB/s. In contrast, Cyclone can
replicate data three ways using 4*10 Gbps commodity ethernet NICs at roughly 3.7
GB/s. Note that this result is with Cyclone running the provable RAFT consensus
protocol, while Mojim is doing simple mirroring of main memory.  One can
conclude that network offload via RDMA and Infiniband is not an a-priori
requirement for high throughput replication. This is made possible by Cyclone's
approach that relieves the CPU from the burden of data copies. On the other
hand, the latency of a hop on commodity ethernet at 5 us with our DPDK stack is
larger than the close to 2us latency with Infiniband. Depending on the use case
for the key value store application the extra 6us with ethernet for the round
trip to the replica might be a concern for some. We note that mapping the
commutativity of key value store interfaces to multiple logs in Cyclone is a
technique that can also be applied to RDMA. Mojim confirms that concurrency is a
significant determinant of performance when replicating over RDMA.

Consensus in a box~\cite{consensus_box} implements the Zookeeper atomic
broadcast protocol together with a NIC on an FPGA. That work ignored durability,
focusing purely on network performance for replication. Latency is excellent due
to the fact that FPGA cuts out the path from CPU caches to the NIC. The authors
report latency as low as 3us for a round trip from leader to follower replica,
compared to the 6us we observe with DPDK. Notably however they reported 7us when
using TCP/IP from the FPGA rather than their own connection oriented network
protocol. On the other hand their peak replication throughput is 4M
replications/sec on 66 Gbps of aggregate network bandwith for small messages,
comparable to the 6M replications/sec mark obtained by Cyclone on an aggregate
40 Gbps of network bandwidth when \emph{also persisting the log on the SSD}. We
believe the general applicability afforded by our software only approach
together with the fact that we provide persistence by design makes it a
compelling alternative to an FPGA based solution, even given the larger
latency. Also, these results demonstrate that a general purpose CPU core can be
as efficient as an FPGA in running a consensus protocol using the techniques
described in this paper.

DARE~\cite{dare} implements state machine replication over RDMA, using a custom
replication protocol. DARE does not consider persistence in its design. It is
worthwhile to point out that since DARE allows any replica to become the leader
it requires a log adjustment protocol for the leader to bring its logs up to
date, a situation we avoid by using RAFT as described in
Section~\ref{sec:dm}. Using 40 Gb/s speeds, and 3-way replication DARE reported
being able to replicate 500K requests/sec. This is without persisting the log of
updates. In contrast, Cyclone replicates upwards of 6 million similarly sized
requests per second with 4*10 Gbps ethernet (without the second level
flashlog). DARE reports an unloaded write latency of 15us, which is lower than
the unloaded write latency of Cyclone at 20us, thanks to Infiniband. The
conclusions we can draw are similar to the comparison with Mojim: a carefully
implemented log replication system obviates the need for network offload when
doing replication.

@@

Cyclone does not provide exactly once semantics as we
believe that exactly once semantics are better provided by the key value store
itself by persisting necessary request markers - as done in systems such as
Kafka~\cite{kafka}. A possible direction of future work however is to add
exactly once semantics to Cyclone's client-server protocol to serve as a
building block for distributed transactions across key-value shards, each
running Cyclone, in a manner similar to other systems~\cite{raft_lin}.
